---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->
```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
library(irg)
```

# irg

R Package for Granger-Causal Analysis of Irregularly Sampled Signals

For users who are interested in having the latest developments, the
GitHub version is ideal although more dependencies are required to run a
stable version of the package. Most importantly, users **must** have a
(C++) compiler installed on their machine that is compatible with R
(e.g. Clang).

```{r, eval=FALSE}
# Install dependencies
install.packages(c("RcppArmadillo","devtools","knitr","rmarkdown"))

# Install the package from GitHub without Vignettes/User Guides
devtools::install_github("SMAC-Group/irg")

# Install the package with Vignettes/User Guides 
devtools::install_github("SMAC-Group/irg", build_vignettes = TRUE)
```

*The setup to obtain the development version of `irg` is platform
dependent.*

## License

The license this source code is released under is the GNU AFFERO GENERAL
PUBLIC LICENSE (AGPL) v3.0. Please see the LICENSE file for full text.
Otherwise, please consult [TLDR
Legal](https://tldrlegal.com/license/gnu-affero-general-public-license-v3-\(agpl-3.0\))
or [GNU](https://www.gnu.org/licenses/agpl-3.0.en.html) which will
provide a synopsis of the restrictions placed upon the
code.
